\thispagestyle{plain}			% Supress header
\section*{Acknowledgements}

First things first, let’s talk about the unsung heroes of this research: the marvelous world of supply chain management. Seriously, who would have thought that the simple act of picking up an onion at the grocery store or receiving a 10-gram letter from halfway across the world would be a result of some of the most intricate and mind-boggling logistics known to humankind? Hats off to the supply chain wizards who orchestrate this beautiful chaos, moving things from here to there with such finesse that we mere mortals can carry on with our onion-chopping and letter-opening without a second thought. 

Of course, we owe a massive thank you to our supervisor Viroj Jienwatcharamongkhol, who not only guided us through the entire research process, but also gave us great ideas to conduct our surveys and interviews. We'd also like to thank our examiner Johanna Börrefors for prompt communication throughout the course. Their patience, wisdom, and occasional eyebrow-raises kept us on track and made this journey far more entertaining than we could have imagined. We’re also immensely grateful to all the professors we’ve learned from throughout this program. Your passion for the subject has been infectious — in the best way possible.

A special shout-out goes to all the online platforms and tools that made remote collaboration a breeze. Let’s be honest, without you, we might have ended up sending research notes by carrier pigeon. Zoom, Teams, Overleaf, Discord — you’ve been the real MVPs, ensuring that we could discuss, debate, and occasionally argue as if we were all in the same room, minus the shared coffee.

And, of course, a heartfelt thank you to our friends and family. You’ve put up with our rants about disrupted supply chains, missed dinners due to late-night SEM analysis, and the endless search for that one tricky citation. Your support, encouragement, and gentle reminders that there is indeed life beyond this thesis have been invaluable. Thanks for keeping us fed, caffeinated, and (mostly) sane.

So here’s to the journey, the chaos, the learning, and to everyone who made this thesis possible — you’re all legends.


\vspace{1.5cm}
\hfill

\authorm \\
\authorp \\
\authort

% \newpage				% Create empty back of side
\thispagestyle{empty}
\mbox{}