\chapter{Appendix 1 - Survey Questionnaire}
\label{appendix:survey}

\noindent Please complete the following questions regarding your company's supply chain management:

\begin{enumerate}[label=\textbf{Q\arabic*:},leftmargin=*]
    \item What type of perishable goods does your company supply? (Select all that apply)\\
    \textit{Perishable goods include any food which is likely to decay faster and has limited shelf life if it's not refrigerated.}
    \begin{enumerate}[label=\arabic*., leftmargin=2em]
        \item Vegetables
        \item Dairy products
        \item Meat and poultry
        \item Seafood
        \item Other: (Please write down)
    \end{enumerate}
    
    \item What is the turnover of your company?\\
    \textit{Annual turnover in terms of USD Million.}
    \begin{enumerate}[label=\arabic*., leftmargin=2em]
        \item Less than 0.5 million USD
        \item Between 0.5 to 2 million USD
        \item Greater than 2 million USD
    \end{enumerate}
    
    \item What is the size of your company?\\
    \textit{In terms of manpower employed.}
    \begin{enumerate}[label=\arabic*., leftmargin=2em]
        \item Small enterprise employing between 10 to 49 persons
        \item Medium enterprise employing between 50 to 249 persons
        \item Large enterprise employing more than 250 persons
    \end{enumerate}
    
    \item To what extent did the COVID-19 pandemic disrupt your supply chain for perishable goods?\\
    \textit{Scale: 1 - Not at all, 5 - Very significantly.}
    
    \item Did your company implement any changes to its supply management strategies during the pandemic?
    \begin{enumerate}[label=\arabic*., leftmargin=2em]
        \item Yes
        \item No
    \end{enumerate}
    
    \item Did you diversify your supplier base for perishable goods in response to the pandemic?
    \begin{enumerate}[label=\arabic*., leftmargin=2em]
        \item Yes
        \item No
    \end{enumerate}
    
    \item How effective were your existing resilience strategies (e.g., inventory management, supplier diversification) in mitigating the impact of the pandemic?
    \textit{Scale: 1 - Not effective at all, 5 - Extremely effective.}
    
    \item Did your company create backup plans for critical parts of the supply chain to ensure continuity during disruptions?
    \begin{enumerate}[label=\arabic*., leftmargin=2em]
        \item Yes
        \item No
    \end{enumerate}
    
    \item Did you adjust your demand forecasting methods to better respond to market changes during the pandemic?
    \begin{enumerate}[label=\arabic*., leftmargin=2em]
        \item Yes
        \item No
    \end{enumerate}
    
    \item Does your company have a formal pandemic preparedness plan in place for future events?
    \begin{enumerate}[label=\arabic*., leftmargin=2em]
        \item Yes
        \item No
    \end{enumerate}
    
    \item We would really appreciate it if you can add some insights based on your personal experience of handling supply chain issues during the pandemic.
    \begin{itemize}[leftmargin=2em]
        \item -- Subjective answer
    \end{itemize}
\end{enumerate}

